---
title: "Upgrading Distill Blog Settings"
description: |
  The second part of a series on how I upgraded this `Distill` themed blog
author:
  - name: Shamindra Shrotriya
    url: https://www.shamindras.com/
date: 2021-12-21
preview: images/step_01_disqus_02.png
categories:
  - features
  - disqus
  - tutorial
  - netlify
  - analytics
output:
  distill::distill_article:
    self_contained: false
    toc: true
    toc_depth: 2
---

> Note: This post was originally written by [Shamindra Shrotriya](https://www.shamindras.com/) and copied here on December 21, 2021 - see the original post [here](https://www.shamindras.com/posts/2019-07-31-shrotriya2019distillpt2/) for a potentially updated version.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
IMAGES_PATH <- here::here(
    "_posts",
    "2021-12-21-upgrading-distill-blog-settings",
    "images")
```

## Step 0: Introduction

This is a meta blogpost and a second-part in a series to describe how I setup
this personal academic blog using the amazing
[distill](https://rstudio.github.io/distill/){target="_blank"} package by the
[RStudio](h//www.rstudio.com/){target="_blank"} team.

The first part of this meta blogpost series can be [found
here](https://www.shamindras.com/posts/2019-07-11-setting-up-a-distill-blog-with-netlify/){target="_blank"},
where I detailed the steps to setup this blog using Netlify and Google Domains.
If you haven't setup a `distill` themed blog then you are encouraged to check
it out before reading this post.

Fortunately `distill` comes with easy to configure settings as well see below.
I've only implemented some of the options available. I should note that the
RStudio `distill` team has already created an [excellent distill blog creation
tutorial](https://rstudio.github.io/distill/blog.html){target="_blank"} which I
thoroughly used and highly recommend to new users to check out.

<aside> Admittedly this blogpost is verbose, but hopefully the details help
**new users** of the `distill` blogging package.  </aside>

With that said, here are some key upgrades I made to this blog.

## Step 1: Setup Disqus comments

I really wanted to setup some comments system for each blogpost. This way I can
learn new tips from readers and find out how to improve posts going forward. I
will go with the recommended [Disqus comments
option](https://disqus.com){target="_blank"} from the [distill
blog](https://rstudio.github.io/distill/blog.html#comments-and-sharing){target="_blank"}.
I simply created a [Disqus](https://disqus.com){target="_blank"} account and
selected **Get Started**. I then clicked the following button to *Install
Disqus on my site*.

<center>
```{r step-01-02-screenshot, fig.cap="Getting Started with Disqus", echo=FALSE, out.extra="class=external", cache=TRUE}
knitr::include_graphics(path =
                            fs::path(IMAGES_PATH,
                                     "step_01_disqus_02.png"))
```
</center>

I was then presented with the following Disqus site configuration menu. I
entered `https:://www.shamindras.com/` for my **Website Name** and manually set
my **Disqus shortname** to be `shamindras-distill` to be easier to remember and
specific to this site, in case I make more websites later on. This Disqus
shortname is important to note down (`r emo::ji("pen")`) as we'll see shortly.

<center>
```{r step-01-03-screenshot, fig.cap="Setup Disqus shortname", echo=FALSE, out.extra="class=external", cache=TRUE}
knitr::include_graphics(path =
                            fs::path(IMAGES_PATH,
                                     "step_01_disqus_03.png"))
```
</center>

After clicking **Create Site** in the previous menu I proceeded to select the
_free_ plan option by subscribing to the *Basic, Free, Ads Supported* comments
option as seen below:

<aside> As a student got to always know when to get a freebie `r
emo::ji("smile")` </aside>

<center>
```{r step-01-04-screenshot, fig.cap="Select Basic (Free, Ads supported) mode", echo=FALSE, out.extra="class=external", cache=TRUE}
knitr::include_graphics(path =
                            fs::path(IMAGES_PATH,
                                     "step_01_disqus_04.png"))
```
</center>


In terms of implementing `Disqus` on my site, I clicked on the following button
to install Disqus on my site manually:

<center>
```{r step-01-05-screenshot, fig.cap="Manual installation of Disqus", echo=FALSE, out.extra="class=external", cache=TRUE}
knitr::include_graphics(path =
                            fs::path(IMAGES_PATH,
                                     "step_01_disqus_05.png"))
```
</center>

Before finishing the manual installation of `Disqus` I ensured that I set the
following configuration options. I particularly like setting an opiononated
comments policy and selected the [Grist Comment
Policy](https://grist.org/grist-comment-policy/){target="_blank"}:

<center>
```{r step-01-06-screenshot, fig.cap="Disqus Configuration Settings", echo=FALSE, out.extra="class=external", cache=TRUE}
knitr::include_graphics(path =
                            fs::path(IMAGES_PATH,
                                     "step_01_disqus_06.png"))
```
</center>

Finally to ensure that the implementation is completed I added the following
line to the `_site.yml` post using the **Disqus shortname** set earlier i.e.
`shamindras-distill` and ensuring `hidden: true` so that the comments are not
expanded by default:

<aside> **Note:** You can see my `_site.yml` with these settings
[here](https://github.com/shamindras/ss_personal_distill_blog/blob/master/_site.yml)
</aside>

```{bash step-01-07, eval=FALSE, echo=TRUE}
collections:
  posts:
    disqus:
      shortname: shamindras-distill
      hidden: true
```

We now see the following comments option at the bottom of every post:

<center>
```{r step-01-07-screenshot, fig.cap="Distill Disqus Comments Selection", echo=FALSE, out.extra="class=external", cache=TRUE}
knitr::include_graphics(path =
                            fs::path(IMAGES_PATH,
                                     "step_01_disqus_07.png"))
```
</center>

You can read more about setting up comments from the official `distill` blog
[here](https://rstudio.github.io/distill/blog.html#comments-and-sharing)

## Step 2: Setup Google Analytics tracking

I also wanted to setup basic user viewing tracking for my site. Fortunately
`distill` can be easily configured to work with [Google
Analytics](https://analytics.google.com/analytics/web){target="_blank"}. In
order to set this up I simply created an account for `Google Analytics` (using
my personal gmail account). I then logged in and selected the option to track
my website as follows:

<center>
```{r step-02-01-screenshot, fig.cap="Google Analytics Settings", echo=FALSE, out.extra="class=external", cache=TRUE}
knitr::include_graphics(path =
                            fs::path(IMAGES_PATH,
                                     "step_02_ga_01.png"))
```
</center>

Note that I specified the **Website Name** field to be `shamindras-distill`.
This is indeed the same as the Disqus shortname from earlier but did not have
to be. I just did it for consistency and easy reference. I was then given a
**Google Analytics token** and concluded this setup by adding the token to the
`_site.yml` file as follows:

<aside> **Note:** You can see my `_site.yml` with these settings
[here](https://github.com/shamindras/ss_personal_distill_blog/blob/master/_site.yml)
</aside>

```{bash step-02-02, eval=FALSE, echo=TRUE}
google_analytics: "UA-145015693-1"
```

You can read more about setting up Google Analytics from the official `distill`
blog [here](https://rstudio.github.io/distill/website.html#google-analytics)

## Step 3: Add Netlify Status Badge

Since [Netlify](https://www.netlify.com){target="_blank"} is the web hosting
platform for my site (see setup details
[here](https://www.shamindras.com/posts/2019-07-11-setting-up-a-distill-blog-with-netlify/#step-8-deploy-your-website){target="_blank"}).
I just logged into my Netlify account and went to my **Site Details** and
obtained the following code from the **Status Badges** option.

<center>
```{r step-03-01-screenshot, fig.cap="Netlify Badge Code", echo=FALSE, out.extra="class=external", cache=TRUE}
knitr::include_graphics(path =
                            fs::path(IMAGES_PATH,
                                     "step_03_netlify_01.png"))
```
</center>

I copy-pasted the above code in at the top of my site `README.md` file. This
let's me quickly know whether my website is up and running as expected by
simply checking out my [github
page](https://github.com/shamindras/ss_personal_distill_blog){target="_blank"}.

<aside> **Note:** You can see my `README.md` with these settings
[here](https://github.com/shamindras/ss_personal_distill_blog/blob/master/README.md)
</aside>

## Step 4: Add blog post sharing options

It is easy to configure distill to allow for easy sharing of posts using a
variety of social media platforms. I allow for **twitter, linkedin, pinterest,
and facebook.** I did this by simply adding the following line in the
`_site.yml` file:

```{bash step-04-01, eval=FALSE, echo=TRUE}
collections:
  posts:
    share: [twitter, linkedin, pinterest, facebook]
```

Now the following sharing options appear at the bottom of every post:

<center>
```{r step-04-01-screenshot, fig.cap="Distill Sharing Options", echo=FALSE, out.extra="class=external", cache=TRUE}
knitr::include_graphics(path =
                            fs::path(IMAGES_PATH,
                                     "step_04_sharing_01.png"))
```
</center>

I also added in the following lines to `_site.yml` to ensure that [twitter
cards](https://rstudio.github.io/distill/metadata.html#twitter-card){target="_blank"}
are correctly generated when posts are shared on twitter:

<aside> **Note:** You can see my `_site.yml` with these settings
[here](https://github.com/shamindras/ss_personal_distill_blog/blob/master/_site.yml)
</aside>

```{bash step-04-02, eval=FALSE, echo=TRUE}
twitter:
  site: "@shamindraas"
  creator: "@shamindraas"
```

## Step 5: Add Corrections/Change Tracking and RSS feed

I frequently make edits to blogposts and intend to do so going forward.
Fortunately `distill` makes it easy **track changes/corrections** made to
blogposts. I did this by simply adding the site repo url to the `_site.yml` as
follows:

```{bash step-05-01, eval=FALSE, echo=TRUE}
repository_url: https://github.com/shamindras/ss_personal_distill_blog
```

Now the following appears at the bottom of all blogposts:

<center>
```{r step-05-01-screenshot, fig.cap="Changes and Corrections Tracking", echo=FALSE, out.extra="class=external", cache=TRUE}
knitr::include_graphics(path =
                            fs::path(IMAGES_PATH,
                                     "step_05_trackcorr_01.png"))
```
</center>

So users can easily track changes or file any concerns as issues, though
hopefully the `Disqus` comment feature makes this easier for everyone.

Finally it is easy to add an **RSS feed** for the blog by simply adding the
following to `_site.yml`:

```{bash step-05-02, eval=FALSE, echo=TRUE}
base_url: https://www.shamindras.com/
navbar:
  left:
    - icon: fa fa-rss
      href: index.xml
```

<aside> **Note:** You can see my `_site.yml` with these settings
[here](https://github.com/shamindras/ss_personal_distill_blog/blob/master/_site.yml)
</aside>

The critical elements are adding in the `base_url` fields and adding in `fa
fa-rss` which is derived from the `index.xml` file.  The `index.xml` file is
automatically generated from the `index.Rmd` when you render the `distill` blog
using the usual command:

```{bash step-05-03, eval=FALSE, echo=TRUE}
rmarkdown::render_site(here::here())
```

## Next Steps

In terms of core `distill` blog settings, these are the main options that I'm
happy to implement for now. For me the next steps are more about **customizing
my own blog workflow**. This will involve setting up utilities to
automatically:

- **Wrap Rmd files** to 80 characters for consistency
- Quickly **delete unused files** e.g. `DS_Store` files on mac
- **Clear knitr cache** for all posts and thoroughly re-render the
site

I expect to do this using a combination of `R` functions/`Makefile` workflow,
but do stay tuned!

## Concluding Thoughts

As it can be seen it is quite easy to customize `distill` for commonly required
features. Really great work by the RStudio team in making such customizations
so user-friendly `r emo::ji("thumbsup")`.
