---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse   = TRUE,
  warning    = FALSE,
  message    = FALSE,
  comment    = "#>",
  fig.path   = "images/",
  fig.retina = 3
)

# Load functions
library(tidyverse)
source(file.path("R", "functions.R"))
```

Welcome to the distillery: a [distill](https://rstudio.github.io/distill/) website showcasing other distill websites and blogs!

If you have a distill blog, we would love you included in this list!
This is an inclusive community of blogs for everyone to learn from. Please,
add yourself!

## How to add your distill blog / website to the showcase:

**Method 1**: [Open an issue](https://github.com/jhelvy/distillery/issues) and note your site `name`, the `url` to your site, and url to the `source` code and we'll add it to the showcase! 

**Method 2**: If you're comfortable working with pull requests, follow these steps: 

1. Fork this repo.
2. Add your site to the `sites.csv` in the root directory (include a `name`, `url` to the site, and url to the `source`).
3. Open the `distillery.Rproj` file and run `build_site.R`.
4. Open a pull request to include your changes!

That's it! Your site will be added to the [showcase](https://jhelvy.github.io/distillery/showcase.html), complete with a screen shot and the links to the site and source.

### List of sites in showcase:

```{r build-content, include=FALSE}
sites <- clean_sites(read_csv("sites.csv"))
rmd_chunks <- make_rmd_chunks(sites, image_width = NULL)
```

```{r insert-sitelist, child = rmd_chunks}
```
