---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

<!-- badges: start -->
[![Render & Deploy Site](https://github.com/jhelvy/distillery/actions/workflows/build_site.yml/badge.svg?branch=main)](https://github.com/jhelvy/distillery/actions/workflows/build_site.yml)
[![Netlify Status](https://api.netlify.com/api/v1/badges/2355cde2-cab8-411b-ad51-e55dd5422c59/deploy-status)](https://app.netlify.com/sites/distillery/deploys)
<!-- badges: end -->

```{r, include = FALSE}
library(tidyverse)
```

Welcome to the [distillery](https://distillery.rbind.io/): a [distill](https://rstudio.github.io/distill/) blog about building distill websites and blogs!

This site was built for the community of distill users to find ways to build and customize their sites and to inspire one another. If you have a distill website or blog, we would love to have it included in the distillery [showcase](https://distillery.rbind.io/showcase.html)! Have a post about ways to customize or add new features to your blog? We would love to have it included on the distillery [tips & tricks page](https://distillery.rbind.io/tips_and_tricks.html)!

This is an inclusive community of blogs for everyone to learn from. Please, add yourself!

# How to contribute

## Add your distill site to the [showcase](https://distillery.rbind.io/showcase.html):

### Method 1

[Open an issue](https://github.com/jhelvy/distillery/issues) and note your site `name`, the `url` to your site, and url to the `source` code and we'll add it to the showcase!

### Method 2

If you're comfortable working with pull requests, follow these steps:

1. Fork this repo.
2. Add your site to the `sites.csv` in the root directory (include a `name`, `url` to the site, and url to the `source`).
3. Open a pull request to include your changes!

That's it! Your site will be automatically added to the [showcase](https://distillery.rbind.io/showcase.html), complete with a screen shot and the links to the site and source!

## Add a post site to the [tips & tricks page](https://distillery.rbind.io/tips_and_tricks.html):

[Open an issue](https://github.com/jhelvy/distillery/issues) and add a link to your post as well as a link to the post source code. We'll copy over the source files and rebuilt the post here, inserting the following attribution statement at the top:

```
> Note: This post was originally written by [name](link) and copied here on {date} - see the original post [here](link) for a potentially updated version.
```

# List of sites in showcase:

```{r insert-sitelist, echo=FALSE, message=FALSE, warning=FALSE}
sites <- read_csv("sites.csv")
sites %>%
  mutate(
    site = paste0("[site](", url, ")"),
    source = paste0("[source](", source, ")"),
  ) %>%
  select(name, site, source) %>%
  arrange(name) %>%
  knitr::kable()
```
