---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

<!-- badges: start -->
[![Render & Deploy Site](https://github.com/jhelvy/distillery/actions/workflows/main.yml/badge.svg?branch=main)](https://github.com/jhelvy/distillery/actions/workflows/main.yml)
<!-- badges: end -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse   = TRUE,
  warning    = FALSE,
  message    = FALSE,
  comment    = "#>",
  fig.path   = "images/",
  fig.retina = 3
)

# Load functions
source(file.path("R", "functions.R"))
```

Welcome to the distillery: a [distill](https://rstudio.github.io/distill/) website showcasing other distill websites and blogs!

If you have a distill blog, we would love to have it included in this list!
This is an inclusive community of blogs for everyone to learn from. Please,
add yourself!

## How to add your distill blog / website to the showcase:

### Method 1

[Open an issue](https://github.com/jhelvy/distillery/issues) and note your site `name`, the `url` to your site, and url to the `source` code and we'll add it to the showcase!

### Method 2

If you're comfortable working with pull requests, follow these steps:

1. Fork this repo.
2. Add your site to the `sites.csv` in the root directory (include a `name`, `url` to the site, and url to the `source`).
3. Open a pull request to include your changes!

That's it! Your site will be automatically added to the [showcase](https://jhelvy.github.io/distillery/showcase.html), complete with a screen shot and the links to the site and source!

### List of sites in showcase:

```{r insert-sitelist, echo=FALSE}
sites <- read_csv("sites.csv")
sites %>% 
  mutate(
    site = paste0("[site](", url, ")"),
    source = paste0("[source](", source, ")"),
  ) %>% 
  select(name, site, source) %>% 
  arrange(name) %>% 
  knitr::kable()
```
