---
title: "Geospatial"
description: "Functions related to the calculation of distance between geographic points and data partitioning in sliding windowsn"
opengraph:
  image: 
    src: "figures_articles/automatic_tabs.png"
  twitter:
    creator: "@rafa_zamr"
    card: summary_large_image
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Geospatial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

ðŸŒ Functions related to the calculation of distance between geographic points and data partitioning in sliding windows.

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  out.width = "100%",
  warning = FALSE,
  message = FALSE
)
```


# Libraries ðŸ“š

```{r }
 library(modeltime)
 library(rsample)
 library(parsnip)
 library(recipes)
 library(workflows)
 library(dplyr)
 library(tidyr)
 library(sknifedatar)
```

## Function sliding_window ðŸ”

This feature allows you to apply a monthly moving sliding window transformation on a data set. The number of folds and the types of variables to be calculated are defined. For a detailed explanation and use case of this function with R code, see [Crime occurrence prediction / sliding_window](https://rafael-zambrano-blog-ds.netlify.app/posts/2020-12-22-prediccin-de-delitos-en-caba/#aplicaci%C3%B3n-de-ventanas-deslizantes).

```{r}
pliegues = 1:13
names(pliegues) = pliegues

variables = c("delitos", "temperatura", "mm_agua", "lluvia", "viento")
names(variables) = variables

sliding_window(data = data_longer_crime %>% dplyr::select(-c(long,lat)),
               inicio = 13,
               pliegues = pliegues,
               variables = variables)
```


## Function pertenencia_punto ðŸ“

Given two sets of geolocated points, this function allows to determine for each point of the first data set, which or which of the points of the second data set are within a certain radius of meters.

* Sample of 100 crimes that occurred in CABA.

```{r}
head(crimes)
```

* 2023 corners of CABA evenly distributed over the city.

```{r}
head(intercepcion_calles)
```

* For each crime, the corner that is within a proximity radius of less than 150 meters is determined.

```{r}
esquina = data.frame(pertenencia_esquina = pertenencia_punto(data = crimes[1:10,], 
                                                             referencia = intercepcion_calles[1:300,],
                                                             metros = 150) %>% 
                       unlist())
```

* Data frame with crimes and their cercaria corners.

```{r}
crimes[1:10,] %>% 
  select(id) %>% 
  bind_cols(esquina)
```

To consult projects where this functions was used, visit:

* [Crime occurrence prediction](https://rafael-zambrano-blog-ds.netlify.app/posts/2020-12-22-prediccin-de-delitos-en-caba/)


